Supplementary materials

### 2018-07-11 WholePlotTrajectories_SuppMat.Rmd
Supp Mat

# Appendix figures

@@

**Figure S2**: Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3 \@ref(fig:FigSeedMassClasses).

\newpage

# **Figure S1**: Bayesian process sheme

@@

# **Figure S2**: Proportion of seed mass classes along time

>>>>

@@

**Figure S2**: Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3 .

@@

### 2018-07-11 WholePlotTrajectories_SuppMat.tex
Supp Mat

\section{Appendix figures}\label{appendix-figures}

@@

\textbf{Figure S2}: Scheme of the redundancy measurement process

\textbf{Figure S3}: Trajectories of seed mass classes proportions over
30 years after disturbance, corresponding to the median (solid line) and
0.025 and 0.975 percentile (gray envelope) observed after 50 iteration
of the taxonomic uncertainty propagation. No gap filling process was
applied in this case. Initial treatments are represented by solid lines
colors with green for control, blue for T1,orange for T2 and red for T3
\ref{fig:FigSeedMassClasses}.

\newpage

\section{\texorpdfstring{\textbf{Figure S1}: Bayesian process
sheme}{Figure S1: Bayesian process sheme}}\label{figure-s1-bayesian-process-sheme}

@@

\section{\texorpdfstring{\textbf{Figure S2}: Redundancy
metric}{Figure S2: Redundancy metric}}\label{figure-s2-redundancy-metric}

{\centering \includegraphics[width=1\linewidth]{ExternalFig/RedundancyMetric}

\caption{Scheme of the redundancy measurement process}\label{fig:RedMM}
\end{figure*}

\section{\texorpdfstring{\textbf{Figure S3}: Proportion of seed mass
classes along
time}{Figure S3: Proportion of seed mass classes along time}}\label{figure-s3-proportion-of-seed-mass-classes-along-time}

>>>>

@@

\textbf{Figure S2}: Trajectories of seed mass classes proportions over
30 years after disturbance, corresponding to the median (solid line) and
0.025 and 0.975 percentile (gray envelope) observed after 50 iteration
of the taxonomic uncertainty propagation. No gap filling process was
applied in this case. Initial treatments are represented by solid lines
colors with green for control, blue for T1,orange for T2 and red for T3
.

@@
